On the Fourier Analysis of Boolean Functions and the Linial-Mansour-Nisan Theorem

### 2020-11-11 CS590/paper.tex
Actually first draft

\begin{lemma}
  Let $f \in \AC^0$ be of depth $d$. Then
  \begin{equation}
    I_f = \mathcal{O}((\log n)^d)
  \end{equation}
\end{lemma}

%    Bibliographies can be prepared with BibTeX using amsplain,
%    amsalpha, or (for "historical" overviews) natbib style.
\bibliographystyle{amsplain}
\bibliography{biblio}

>>>>

\begin{lemma} \label{influence}
  Let $f \in \AC^0$ be of depth $d$. Then
  \begin{equation}
    I_f = \mathcal{O}((\log n)^d)
  \end{equation}
\end{lemma}

Lemma (\ref{influence}) shows that functions in $\AC^0$  are not suitable for constructing universal hash functions (\cite{mansour}) and pseudorandom function generators (\cite{lmn}). We give a rough definition and sketch based on the treatment found in (\cite{lmn}.

\begin{definition}
  A function $f:\{0,1\}^m \times \{0,1\}^n \rightarrow \{0,1\}$ is called a \emph{pseudorandom function generator} if there exists no polynomial-time oracle Turing machine which can distinguish between the outputs from a true random oracle versus $f(s,_)$ for some random seed $s \in \{0,1\}^m$.
\end{definition}

\begin{lemma}
  No pseudorandom function generators exist in $\AC^0$
\end{lemma}
By taking advantage of the low average sensitivity, we can simply perturb the input slightly and check if the output of $f$ changes. If it doesn't, there is a good chance that
it lies in $\AC^0$.

\begin{remark}{(\emph{Some concluding remarks})}
  It is worth noting that the bounds shown by Linai-Mansour-Nisan have been improved by Tal (\cite{tal}). Specifically, he showed that for any $n$-ary boolean function $f$ with size $M$ and depth $d$,\
  \begin{equation}
    \sum_{|S| > t} |\hat{f}(S)|^2 = 2^{\Omega(k/\log^{d-1}{M})}
  \end{equation}
\end{remark}
%    Bibliographies can be prepared with BibTeX using amsplain,
%    amsalpha, or (for "historical" overviews) natbib style.
\bibliographystyle{amsplain}
\bibliography{biblio}
